\documentclass[a4paper]{article}

\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
%[ansinew]

% line spacing
\renewcommand{\baselinestretch}{0.8} 

% \usepackage{fontspec}
% \setmainfont{Calibri}
% \setsansfont{Ubuntu}% Ubuntu as sans - use \sffamily or \textsf{} as normal
% \setmonofont{JetBrainsMono Nerd Font Mono}% Ubuntu Mono as 'typewriter' - use \ttfamily or \texttt{}

\hypersetup{
  colorlinks = true, %Colours links instead of ugly boxes
  urlcolor   = blue, %Colour for external hyperlinks
  linkcolor  = blue, %Colour of internal links
  citecolor  = true %Colour of citations, could be ``red''
}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\huge{Shivanshu}} \\
    Dehradun, India |
    +91 9368850911 |
    \href{mailto://semwalshivanshu@gmail.com}{semwalshivanshu@gmail.com}\\
    \href{https://www.linkedin.com/in/shivanshu-semwal/}{LinkedIn} |
    \href{https://github.com/shivanshu-semwal}{GitHub} |
    \href{https://shivanshu-semwal.github.io/}{Portfolio} |
    \href{https://leetcode.com/semwalshivanshu/}{Leetcode} |
\end{center}

\subsubsection*{EDUCATION}
% \vspace{1pt}
\hrule
\vspace{10pt}

\noindent
\textbf{GRAPHIC ERA UNIVERSITY - Dehradun, India} \hfill  \textit{July 2019 - June 2023} \\
Bachelor of Technology, Computer Science \& Engineering \hfill \textit{Cumulative GPA: 9.53/10} \\

\noindent
\textbf{DAV Public School - Dehradun, India} \hfill \textit{March 2017 - March 2019} \\
Higher Secondary Education \hfill \textit{92.00 \%} \\

\noindent
\textbf{Carman School - Dehradun, India} \hfill \textit{March 2015 - March 2017} \\
Secondary Education \hfill \textit{92.14 \%}

\subsubsection*{WORK EXPERIENCE}
% \vspace{1pt}
\hrule
\vspace{10pt}

\noindent
\textbf{SAMSUNG RESEARCH INSTITUTE BANGALORE - Remote} \\
\textit{PRISM Research Intern} \hfill \textit{Sept 2021 - Jan 2022}
\begin{itemize} [leftmargin=*,nosep]
    % \setlength\itemsep{0.01em}
    \item Led a team of three individuals researching about Matter specification.
    \item Tested SmartThings SDK and integrated it with matter build with with on Tizen/Ubuntu Platform
    \item Communicated the findings with Samsung Mentors and worked on their Feedback.
\end{itemize}

\subsubsection*{PROJECTS}
% \vspace{1pt}
\hrule

\vspace{10pt}
\noindent
\textbf{Auction Management System} \\
\textit{Built Using - django, python, bootstrap}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Objective:} To built a web app which provides functionality for conducting online auctions.
    \item Seller can set time for the auction to start and end, and set the minimum cost for bidding.
          Bidders can then bid on the product and bidder with highest bid wins.
\end{itemize}

\vspace{10pt}
\noindent
\textbf{Hand Gesture Recognition} \\
\textit{Built Using - Python, TensorFlow, Keras, opencv}
\begin{itemize} [leftmargin=*, nosep]
    \item \textbf{Objective:} To determine the hand gesture from video feed in real time.
    \item Used image segmentation and convolutional neural networks.
    \item Have a data generation module, to generate training data.
\end{itemize}

\vspace{10pt}
\noindent
\textbf{Recipe Recommendation System} \\
\textit{Built Using - NeO4j, nodejs, expressjs, w3css}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Objective:} Based on availability of ingredients with a user this application
          helps discover the list of possible dishes with theses ingredients.
    \item Uses modern graph database - NeO4j, to make links between ingredients and dishes.
\end{itemize}

\vspace{10pt}
\noindent
\textbf{Hand Digit Recognition} \\
\textit{Built Using - tensorflow, python, p3.js, tf.js}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Objective:} Predict handwritten digit form the provided image.
    \item Created a model using CNN with an accuracy of 99.0\%
    \item Converted model to json format, used tf.js to load model and make predictions in web app.
\end{itemize}


\subsubsection*{TECHNICAL SKILLS}
% \vspace{1pt}
\hrule
\vspace{10pt}
\textbf{Languages: } C, C++, Java, Python, Scala, Cypher, SQL, javascript, HTML, CSS \\
\textbf{Databases: } MySQL, MongoDB, NeO4j \\
\textbf{Frameworks and Libraries: } flask, django, TensorFlow, streamlit \\
\textbf{Tools and Software: } node.js, Hadoop, \LaTeX, Tableau, VSCode \\
\textbf{Cloud Platforms: } AWS, Azure, GCP \\
\textbf{VCS: } git

\subsubsection*{ACHIEVEMENTS}
% \vspace{1pt}
\hrule
\vspace{10pt}

\begin{itemize}[leftmargin=*, nosep]
    \item \noindent \textbf{Participated in D.A.V National Sports} \textit{Won cluster and zonal level chess events and participated in D.A.V National Sports, 12 Dec - 14 Nov 2018}
    \item \noindent \textbf{Intellinovation AI Hackathon GEU, 2021 2nd place} \textit{Developed \href{https://www.github.com/Bot-7037/Ventilator-Pressure-Prediction}{Ventilator Pressure Prediction}
              which uses deep learning mechanism to automate the ventilators used in hospitals.}
    \item Solved over 1000 competitive programming problems so far on platforms like Leetcode and HackerRank.
    \item Complete Google Cloud Foundations Course on qwikilabs, Data Science Fundamentals, Artificial Intelligence, \\
          Apache Sparks and SQL courses on Coursera and other certifications related to various programming languages.
\end{itemize}

\end{document}
